---
title: "p8105_hw1_cm4070"
author: Claire Mobley
date: 2021-09-30
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```
# Problem 1 

### Create a data frame 

_This code creates a data frame with numeric, logical, character, and factor variables._

```{r dataframe_problem1, message=FALSE}

set.seed(1234)

problem1_df = tibble(
  x = rnorm(10),
  vec_logical = x > 0, 
  vec_char = c("Hi", "my", "name", "is", "Claire", "Mobley", "nice", "to", "meet", "you"), 
  vec_factor = factor(c("red", "yellow", "green", "red", "yellow", "green", "yellow", "green", "green", "green"))
)

problem1_df
```

### Compute the mean of each variable

_This code attempts to compute the mean of x, vec_logical, vec_char, and vec_factor variables._

```{r means_problem1, message=FALSE, warning=FALSE}
library(tidyverse)

mean(pull(problem1_df, x))

mean(pull(problem1_df, vec_logical))

mean(pull(problem1_df, vec_char))

mean(pull(problem1_df, vec_factor))
```

* The mean of x is `r mean(pull(problem1_df, x))`

* The mean of vec_logical is `r mean(pull(problem1_df, vec_logical))`

* The mean of vec_char is `r mean(pull(problem1_df, vec_char))`

* The mean of vec_factor is `r mean(pull(problem1_df, vec_factor))`

The numeric and logical variables work. 

The character and factor variables do not work. 

### Convert variables 

_This code attempts to convert the vec_logical, vec_char, and vec_factor variables to numeric form._

```{r numeric_problem1, eval = FALSE}
as.numeric(pull(problem1_df, vec_logical))

as.numeric(pull(problem1_df, vec_char))

as.numeric(pull(problem1_df, vec_factor))
```

The as.numeric function creates a double-precision vector of the specified length with each element as 0. 

* The logical vector turns into numericals with 0 as false and 1 as true. 

* The factor vector turns into numericals 1 through 3 for 3 levels.

* The character vector is unable to be interpreted in numericals because it is only characters. 

The factor and character means could not be computed because they are either meaningless or cannot be made numerical.

# Problem 2 

### New dataset 

_This code will load the `penguins` dataset._

```{r dataset_problem1}
data("penguins", package = "palmerpenguins")

penguins
```

### Description

* `penguins` dataset contains 8 variables: `r names(penguins)` 

* contains `r nrow(penguins)` rows and `r ncol(penguins)` columns

* the mean flipper length is `r mean(na.rm=TRUE, pull(penguins, flipper_length_mm))` 

### Scatterplot

_This code will make a color coded scatter plot of flipper length vs. bill length for the species variable._

```{r ggplot_species, warning=FALSE}
ggplot(penguins, aes(x = flipper_length_mm, y = bill_length_mm, color = species)) + geom_point()

```





