---
title: "p8105_hw1_cm4070"
author: Claire Mobley
date: 2021-09-30
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Problem 1 

This code creates a data frame.

### Create a data frame 

```{r dataframe_problem1, message=FALSE}

set.seed(1234)

problem1_df = tibble(
  x = rnorm(10),
  vec_logical = x > 0, 
  vec_char = c("Hi", "my", "name", "is", "Claire", "Mobley", "nice", "to", "meet", "you"), 
  vec_factor = factor(c("red", "yellow", "green", "red", "yellow", "green", "yellow", "green", "green", "green"))
)

problem1_df
```

This code will compute the means of data frame 
variables. 

### Compute the mean of each variable

```{r means_problem1, message=FALSE, warning=FALSE}
library(tidyverse)

mean(pull(problem1_df, x))

mean(pull(problem1_df, vec_logical))

mean(pull(problem1_df, vec_char))

mean(pull(problem1_df, vec_factor))
```

This code provides the below computations. The numeric and logical variables work. The character and factor variables do not work. 

* The mean of x is `r mean(pull(problem1_df, x))`

* The mean of vec_logical is `r mean(pull(problem1_df, vec_logical))`

* The mean of vec_char is `r mean(pull(problem1_df, vec_char))`

* The mean of vec_factor is `r mean(pull(problem1_df, vec_factor))`

